Market simulator

### 2020-11-28 analysis/05_market_simulator.Rmd
Changed default configuration file names and cleaned up some of the comments after testing

```{r load-data, message=FALSE}

# Gammas of the "everything" model
gammas <- read_rds(
  here::here('analysis', 'output', 'posterior_draws', 'public_political_social_charity_demo.rds')
  ) %>% 
  group_by(i, j) %>% 
  summarize(gamma_mean = mean(Gamma)) %>% 
  ungroup() %>% 
  pivot_wider(names_from = j, values_from = gamma_mean) %>% 
  select(-i) %>% 
  t()

# Default Configurations

# Organization
org_default <- read_csv(
    here::here('analysis', 'output', 'configurations', 'organization_config01.csv')
  )

# Persona
per_default <- read_csv(
    here::here('analysis', 'output', 'configurations', 'persona_config01.csv')
  )

# Organization configuration
# organization_data <- reactive({
#   if (is.null(input$org_update$datapath)) {
#     organization_data <- org_default
#   } else {
#     req(input$org_update)
#     organization_data <- read_csv(input$org_update$datapath)
#   }
# })

# Persona configuration
# persona_data <- reactive({
#   if (is.null(input$per_update$datapath)) {
#     persona_data <- read_csv(
#       here::here('analysis', 'output', 'configurations', 'persona_config01.csv')
#     )
#   } else {
#     req(input$per_update)
#     persona_data <- read_csv(input$per_update$datapath)
#   }
# })

```

@@

Imports
--------------------------------------

```{r import}
# let the user choose the type of input file
radioButtons(
  inputId = "what_config",
  label = "Choose Configuration",
  choices = c("Default", "User input"),
  selected = "Default",
  inline = FALSE
  )

# render file input widgets conditioned on user choice

# Organization file input
conditionalPanel(condition = 'input.what_config == "User input"',
                 fileInput(
                   "org_update",
                   "Import Organization Data",
                   accept = c(
                     "text/csv",
                     "text/comma-separated-values,text/plain",
                     ".csv"
                   )
                  ),
                 actionButton(
                   "org_button",
                   label = "Update Organization Data"
                  )
                 )

# Persona file input
conditionalPanel(condition = 'input.what_config == "User input"',               
                fileInput(
                  "per_update",
                  "Import Persona Data",
                  accept = c(
                    "text/csv",
                    "text/comma-separated-values,text/plain",
                    ".csv"
                  )
                ),
                actionButton(
                  "per_button",
                  label = "Update Persona Data"
                )
              )

# deal with the file selected by the user

# Organization Configuration
organization_data <- reactive({
  if (input$what_config == "Default") {
    x <- org_default
  } else {
    if (input$what_config == "User input") {
      req(input$org_button)
      req(input$org_update)
      x <- read_csv(input$org_update$datapath)
    }
  }
})

# Persona Configuration
persona_data <- reactive({
  if (input$what_config == "Default") {
    x <- per_default
  } else {
    if (input$what_config == "User input") {
      req(input$per_button)
      req(input$per_update)
      x <- read_csv(input$per_update$datapath)
    }
  }
})

```

Configurations
--------------------------------------------------

@@

@@

```{r export}
# Render the organization configurations as a table
renderTable({
  org_choice = org_reactive()
  org_choice
})

# Download Button
downloadButton("download_org", label = "Download Organization Data")

@@

# Render the persona configurations as a table
renderTable({
  per_choice = per_reactive()
  per_choice
})

# Download Button
downloadButton("download_per", label = "Download Persona Data")

>>>>

```{r load-data, message=FALSE}
# Gammas of the "everything" model
gammas <- read_rds(
    here::here('analysis', 'output', 'posterior_draws', 'public_political_social_charity_demo.rds')
  ) %>% 
  group_by(i, j) %>% 
  summarize(gamma_mean = mean(Gamma)) %>% 
  ungroup() %>% 
  pivot_wider(names_from = j, values_from = gamma_mean) %>% 
  select(-i) %>% 
  t()

# Default configurations
org_default <- read_csv(
    here::here('analysis', 'output', 'configurations', 'org_data_default.csv')
  )
per_default <- read_csv(
    here::here('analysis', 'output', 'configurations', 'per_data_default.csv')
  )
```

@@

Configurations
-------------------------------------------------

@@

Import
-------------------------------------------------

```{r import}
# Organization configuration import
fileInput(
 "org_update",
 "Import Organization Data",
 accept = c(
   "text/csv",
   "text/comma-separated-values,text/plain",
   ".csv"
 )
)
actionButton(
 "org_button",
 label = "Update Organization Data"
)

# Persona configuration import
fileInput(
  "per_update",
  "Import Persona Data",
  accept = c(
    "text/csv",
    "text/comma-separated-values,text/plain",
    ".csv"
  )
)
actionButton(
  "per_button",
  label = "Update Persona Data"
)

# Use the default configurations if no inputs are provided
organization_data <- reactive({
  if (is.null(input$org_update$datapath)) {
    x <- org_default
  } else {
    req(input$org_button)
    req(input$org_update)
    x <- read_csv(input$org_update$datapath)
  }
})

persona_data <- reactive({
  if (is.null(input$per_update$datapath)) {
    x <- per_default
  } else {
    req(input$per_button)
    req(input$per_update)
    x <- read_csv(input$per_update$datapath)
  }
})
```

@@

```{r export}
# Render the organization configuration as a table
renderTable({
  org_choice = org_reactive()
  org_choice
})

# Download organization configuration
downloadButton("download_org", label = "Download Organization Data")

@@

# Render the persona configuration as a table
renderTable({
  per_choice = per_reactive()
  per_choice
})

# Download persona configuration
downloadButton("download_per", label = "Download Persona Data")
